---
title: "Incarceration and a National Inbalance in Power"
author: "Zahra Firoz"
date: 'November 27th 2022'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 
This analysis uses data provided by The Vera Institute regarding incarceration rates across The United States. The data was originally released in 2015 and then updated in 2019. Using this data I will draw conclusions using functions and graphs by applying various R tools and packages. 

Recall that _{r echo=TRUE}_ can be used to display the code, 
which is very useful when developing and debugging a report. Here's an example: 

```{r echo=TRUE}
num <- 5
sum <- sum(test_query2(num))
print(sum)
```

## Introduction 
There is a serious problem with the incarceration system within the United States. Most importantly there are issues and inequalities in this system regarding issues of race, gender, color, and more. When we incarcerate people at uneven rates there is a clear violation of human rights, freedoms, and a mishandling and faulty division of power. The Vera website has determined that people of color, more specifically black people, are two times more likely to be incarcerated than white people. This statistic alongside other very serious ones listed on the Vera website show that the direct stakeholders of this social issue are US Citizens and Immigrants, people of color, and government figures such as police. The indirect stakeholders are people working in the prison system, families of those incarcerated, and the communities they are tied to. This report will encapsulate important information and offer insight on the growth of the prison population by nation and state, reveal patterns of inequality, and lastly a visualization showing how the inequalities vary geographically. 

## Data Summary 
[TODO]

[TODO ... other sections ... See Canvas for details]

_All the very best with your work!_

